### 2025-11-12 Paper/paperdraft_fall2025.tex
Updates from Overleaf

    The estimated difference in readmission and mortality rates between hospitals with and without clinical executives are shown in Figure \ref{fig:clinicalsynthdid}. Estimate $\beta$ is represented in the difference in slope after 2012 when pay-for-performance incentives began. Panel \ref{fig:read_synth_clinical} shows the estimated difference in readmission rates, and reveals that non-clinical teams decrease readmissions by .3 (standard error .13) more than clinical teams. This is a relatively small magnitude given an average readmission rate of 21. However, \citeauthor{gupta2021impacts} (\citeyear{gupta2021impacts}) finds that hospitals overall decrease readmissions by around 3 percentage points due to the program, so this reveals a meaningful difference in behavior relative to the overall behavior change. In panel \ref{fig:mort_synth_clinical}, I show the estimated difference in mortality for always clinical and never clinical leadership teams after 2012. While the magnitude of the difference is similar to that for readmission rates (relative to the mean), mortality is a noisy measure, and I cannot rule out null effects.

@@

>>>>

    The estimated difference in readmission and mortality rates between hospitals with and without clinical executives are shown in Figure \ref{fig:clinicalsynthdid}. Estimate $\beta$ is represented in the difference in slope after 2012 when pay-for-performance incentives began. Panel \ref{fig:read_synth_clinical} shows the estimated difference in readmission rates, and reveals that non-clinical teams decrease readmissions by .3 (standard error .13) more than clinical teams. This is a relatively small magnitude given an average readmission rate of 21. However, \citeauthor{gupta2021impacts} (\citeyear{gupta2021impacts}) finds that hospitals overall decrease readmissions by around 3 percentage points due to the program, so this reveals a meaningful difference in behavior relative to the overall behavior change. Using estimates from \citeauthor{gupta2021impacts} (\citeyear{gupta2021impacts}), a 1 percentage point reduction in readmissions across three penalized conditions corresponds to approximately \$110 million in avoided Medicare reimbursements annually. Our results indicate that hospitals led by non-clinical executive teams achieve an additional 0.3 percentage point reduction in readmissions compared to those led by clinical teams. Under the same assumptions, this differential accounts for roughly \$33 million in annual avoided spending—equivalent to 30\% of the savings associated with a 1 percentage point reduction for these conditions. This back-of-the-envelope calculation reflects the incremental contribution of leadership composition to payer-side savings.

    In panel \ref{fig:mort_synth_clinical}, I show the estimated difference in mortality for always clinical and never clinical leadership teams after 2012. While the magnitude of the difference is similar to that for readmission rates (relative to the mean), mortality is a noisy measure, and I cannot rule out null effects.

@@

    \subsection{Clinical CEO}

    \begin{figure}[ht!]
     \caption{Effect of CEO Clinical Training on Readmission and Mortality Rates}
     \centering
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \caption{Readmission Rate}
         \includegraphics[width=\textwidth]{Objects/ceo_read_md_nomd_synth_graph.pdf}
         \label{fig:ceo_read_synth_clinical}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \caption{Mortality Rate}
         \includegraphics[width=\textwidth]{Objects/ceo_mort_md_nomd_synth_graph.pdf}
         \label{fig:ceo_mort_synth_clinical}
     \end{subfigure}
        \label{fig:ceo_clinicalsynthdid}
    \end{figure}
